---
title: "Analysis: using comstab with MCR fish data"
author: "Julianna Renzi"
date: "2025-07-12"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}
# Clear environment for maximum reproducibility
rm(list=ls())

# load librarian (package for installing/loading packages)
if (!require("librarian")) install.packages("librarian")

# Load other necessary libraries
librarian::shelf(here, # relative file paths
                 tidyverse, # data wrangling
                 vegan, # community analyses/diversity/etc.
                 patchwork # plotting
)
```

# Bring in data

```{r}
# fish biomass
mcr_fish <- read_csv(here("CSVs", "data_cleaned", "mcr_fish_biomass_5x50m2.csv"))

# fish grouping metadata
mcr_meta <- read_csv(here("CSVs", "taxa_tables", "mcr_fish_fishbase.csv")) %>%
  # NOTE: This means the taxonomy will be outdated! just doing this for now
  mutate(taxon_name = Taxonomy)

```

# Source Reilly's functions

```{r}
source(here("R", "functions", "00_Functions.R"))
```

Geometric mean function

```{r}
CalcZeroInfGeomDens = function(x){
  prob_obs = sum(x > 0)/length(x)
  geom_mean_dens = ifelse(prob_obs > 0, exp(mean(log(x[x > 0]))), 0)
  return(geom_mean_dens * prob_obs)
}
```

# Set graphing theme

```{r set graphing theme}
# ggplot theme
theme_set(
  theme_bw(base_size = 20) +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
) 
```

# Get data into year-species matrix

```{r}
mcr_fish %>% 
  group_by(dataset, site, habitat, year, plot, taxon_name) %>% 
  summarize(mean_biomass_g_per_5x50m2 = mean(biomass_g_per_5x50_m2)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = taxon_name, values_from = mean_biomass_g_per_5x50m2,
              values_fill = 0) -> mcr_wide
```

# Create a subsetting function so we can be flex with communities

First get a key for all the sites/habiats/years so we'll always fill zeros

```{r}
mcr_wide %>% 
  select(dataset, site, habitat, year, plot) -> mcr_key
```

Make a function for selecting a subgroup

```{r}
subset_mcr_group <- function(df_long, meta_df, filter_column, condition) {
  
  # join the df with the metadata with grouping variables
  df_long %>% 
    full_join(meta_df) %>% 
    # get rid of any NA columns in the column of interest (e.g., taxa not identified to the species-level)
    filter(.data[[filter_column]] != "na") %>% 
    filter(!is.na(.data[[filter_column]]))  %>% 
    filter(.data[[filter_column]] == condition)  %>% 
    group_by(dataset, site, habitat, year, plot, taxon_name) %>% 
    summarize(mean_biomass_g_per_5x50m2 = mean(biomass_g_per_5x50_m2)) %>% 
    ungroup() %>% 
    pivot_wider(names_from = taxon_name, values_from = mean_biomass_g_per_5x50m2,
                values_fill = 0)  %>% 
    # join to account for any zeros
    full_join(mcr_key) %>% 
    # replace with zeros
    mutate(across(everything(), ~replace(., is.na(.), 0))) -> df_wide
    # fill zeros if present (need to add when we get wifi)
    
  df_wide
    
}
```

# Overall MCR fish stats

## Get community diversity stats function

```{r}
get_mcr_diversity <- function(df_wide) {
  # df_wide should have dataset, site, habitat, year, and plot variables as columns but nothing else metadata-wise
  # get metadata to add to the diversity calculations
  df_wide %>% 
    select(dataset, site, habitat, year, plot) -> div_mat
    
  # create species matrix
  df_wide %>% 
    select(-dataset, -site, -habitat, -year, -plot) -> spp_mat
  
  # add information
  div_mat$richness <- specnumber(spp_mat)
  div_mat$shannon <- diversity(spp_mat, index = "shannon")
  div_mat$evenness <- div_mat$shannon/log(div_mat$richness)
  div_mat$total_biomass <- rowSums(spp_mat)
  
  div_mat
}
```

## Plot community stats functions

```{r}
plot_mcr_diversity <- function(df_diversity, title_text){
  # df_diversity should be the output from get_mcr_diversity()
  # first re-level for plotting purposes
  df_diversity %>% 
    mutate(habitat = factor(habitat, levels = c("forereef", "backreef", "fringing"))) -> df_diversity
  
  # first for richness
  df_diversity %>% 
    ggplot(aes(x = year, y = richness, color = habitat)) +
    geom_line() +
    facet_wrap(.~site) +
    scale_colour_viridis_d() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1)) -> plt.a
  
  # evenness
  df_diversity %>% 
    ggplot(aes(x = year, y = evenness, color = habitat)) +
    geom_line() +
    facet_wrap(.~site) +
    scale_colour_viridis_d() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))  -> plt.b
  
  # Shannon
  df_diversity %>% 
    ggplot(aes(x = year, y = shannon, color = habitat)) +
    geom_line() +
    facet_wrap(.~site) +
    scale_colour_viridis_d() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1)) -> plt.c
  
  # total biomass
  df_diversity %>% 
    ggplot(aes(x = year, y = total_biomass, color = habitat)) +
    geom_line() +
    facet_wrap(.~site) +
    scale_colour_viridis_d() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) -> plt.d
  
  (plt.a + plt.b) / (plt.c + plt.d) + plot_annotation(
    title = title_text,
    theme = theme(
      plot.title = element_text(face = "bold", vjust = 0.5),
    )
  )
}
```

## Make diversity plots

Overall species diversity

```{r make PDF}
# Overall species diversity
plot_mcr_diversity(get_mcr_diversity(mcr_wide), title_text = "All fish species") -> plt.all.div
```

By coarse trophic groups

```{r piscivores}
# just piscivores
plot_mcr_diversity(get_mcr_diversity(
  subset_mcr_group(df_long = mcr_fish, meta_df = mcr_meta, 
                   filter_column = "CoarseTrophicMCR", 
                   condition = "Piscivore_primarily")
  ), 
  title_text = "Piscivores") -> plt.pisc.div

```

```{r primary consumers}
# just primary consumers
plot_mcr_diversity(get_mcr_diversity(
  subset_mcr_group(df_long = mcr_fish, meta_df = mcr_meta, 
                   filter_column = "CoarseTrophicMCR", 
                   condition = "Primary Consumer")
  ), 
  title_text = "Primary consumers") -> plt.primcon.div
```

```{r Planktivore}
plot_mcr_diversity(get_mcr_diversity(
  subset_mcr_group(df_long = mcr_fish, meta_df = mcr_meta, 
                   filter_column = "CoarseTrophicMCR", 
                   condition = "Planktivore")
  ), 
  title_text = "Planktivore") -> plt.plankt.div
```


```{r Secondary Consumer}
plot_mcr_diversity(get_mcr_diversity(
  subset_mcr_group(df_long = mcr_fish, meta_df = mcr_meta, 
                   filter_column = "CoarseTrophicMCR", 
                   condition = "Secondary Consumer")
  ), 
  title_text = "Secondary Consumer") -> plt.seccon.div
```

## Make PDF of all the plots

```{r}
pdf(here("figures", "mcr_fish_diversity_time.pdf"), width = 17, height = 10)

print(plt.all.div)
print(plt.primcon.div)
print(plt.seccon.div)
print(plt.plankt.div)
print(plt.pisc.div)

dev.off()
```

# All time MCR CVs

## Make functions to get CV stats for MCR sites

First a general partitioning function, which we'll mainly use in the next function, which allows us to do this for multiple sites/communities

```{r}
partition_mcr <- function(df_wide, condition) {
  # 'condition' should be an expression to filter for that can be evaluated in the context of df (HABITAT/SITE/COMMUNTIY)
  # df_wide should be a species matrix with the normal metadata (dataset, site, habitat, plot)
  
  # filter df for the site/community we are interested in
  df_wide %>% 
    filter(plot == condition) %>%
    select(-dataset, -site, -habitat, -plot) %>% 
    rename(Year = year) -> df_2
  
  # get partitionR results
  part <- partitionR(as.matrix(df_2)) 
  # get warnings to store
  captured <- capture_warnings(partitionR(as.matrix(df_2)))
  
  cbind(data.frame("Community" = as.character(condition)), 
        t(as.data.frame(part$CVs)), t(as.data.frame(part$Stabilization)),
        t(as.data.frame(part$Relative)), t(as.data.frame(part$TPLs)), 
        data.frame("Warnings" = str_c(captured$warnings, collapse = "PLUS "))) -> df_3
  
  rownames(df_3) <- NULL
  df_3
}
```

Iterate over a list of MCR sites

```{r}
partition_many_mcr <- function(df_wide, conditions) {
  # initialize the dataframe
  megadf <- partition_mcr(df_wide, conditions[1])
  
  # iterate over each site
 for(i in 2:length(conditions)) {
   megadf <- rbind(megadf, partition_mcr(df_wide, conditions[i]))
 }
  
  # add metadata
  megadf %>% 
    as.data.frame() %>% 
    rowwise() %>% 
    mutate(Site = paste0("LTER_", str_split(Community, "_")[[1]][2])) %>% 
    mutate(Habitat = str_split(Community, "_")[[1]][3])
}

```

Also make a plotting function

```{r}
plot_mcr_CVs <- function(cv_df, title_text) {
  # cv_df is the output from a partition_many_mcr function
  cv_df %>% 
    select(Community, Site, Habitat, CVe, CVtilde, CVa, CVc) %>% 
    pivot_longer(cols = c("CVe", "CVtilde", "CVa", "CVc"), names_to = "Component", values_to = "CV") %>% 
    mutate(CV = as.numeric(CV)) %>% 
    group_by(Habitat, Component) %>% 
    summarize(mean_CV = mean(CV),
              se = sd(CV)/sqrt(n())) %>% 
    # re-level so they match
    mutate(Component = factor(Component, levels = c("CVe", "CVtilde", "CVa", "CVc")),
           Habitat = factor(Habitat, levels = c("forereef", "backreef", "fringing"))) %>% 
    ggplot(aes(x = Component, y = (mean_CV), group = Habitat, color = Habitat)) +
    geom_point(size = 3) +
    scale_x_discrete(labels = c("CVa" = expression("CV"[a]), 
                                                   "CVc" = expression("CV"[c]), 
                                                   "CVe" = expression("CV"[e]), 
                                                   "CVtilde" = expression(tilde("CV")))) +
    geom_errorbar(aes(ymin = (mean_CV - se), ymax = (mean_CV + se)), width = 0.2) +
    geom_line() +
    scale_colour_viridis_d() +
    labs(title = title_text) +
    theme(plot.title = element_text(vjust = 0.5))
 
}
```

## Make CV plots for coarse trophic groupings

First for all species

```{r}
mcr_alltime <- partition_many_mcr(df = mcr_wide, conditions = unique(mcr_wide$plot))

plot_mcr_CVs(mcr_alltime, "All species") -> plt.all.cv
```

Then by coarse trophic groups. First, Piscivores:

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "CoarseTrophicMCR", 
                                           condition = "Piscivore_primarily"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "Piscivores"
) -> plt.pisc.cv
```

Primary consumers

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "CoarseTrophicMCR", 
                                           condition = "Primary Consumer"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "Primary consumers"
) -> plt.primcon.cv
```

Secondary consumers

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "CoarseTrophicMCR", 
                                           condition = "Secondary Consumer"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "Secondary consumers"
) -> plt.seccon.cv
```

Planktivores

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "CoarseTrophicMCR", 
                                           condition = "Planktivore"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "Planktivores"
) -> plt.plankt.cv
```

## Make CV plots for estimated trohpic bin groupings

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "TrophicBinEst", 
                                           condition = "2-2.49"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "TL: 2-2.49"
) -> plt.2.249.cv
```

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "TrophicBinEst", 
                                           condition = "2.5-2.99"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "TL: 2.5-2.99"
) -> plt.25.299.cv
```

3-3.49

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "TrophicBinEst", 
                                           condition = "3-3.49"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "TL: 3-3.49"
) -> plt.3.349.cv
```

3.5-3.99

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "TrophicBinEst", 
                                           condition = "3.5-3.99"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "TL: 3.5-3.99"
) -> plt.35.399.cv
```

4-4.49

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "TrophicBinEst", 
                                           condition = "4-4.49"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "TL: 4-4.49"
) -> plt.4.449.cv
```

4.5-5.99: **TOO FEW SPECIES**

```{r}
plot_mcr_CVs(
  partition_many_mcr(df = subset_mcr_group(df_long = mcr_fish, 
                                           meta_df = mcr_meta, 
                                           filter_column = "TrophicBinEst", 
                                           condition = "4.5-5.99"), 
                     conditions = unique(mcr_wide$plot)),
  title_text = "TL: 4.5-5.99"
) #-> plt.45.599.cv
```

## Output all CV figures into a PDF

```{r}
pdf(here("figures", "CV_plots_alltime.pdf"), height = 12, width = 14)

print((plt.all.cv + plot_spacer( )) / 
  (plt.primcon.cv + plt.seccon.cv) / 
    (plt.pisc.cv + plt.plankt.cv) )


print((plt.2.249.cv + plt.25.299.cv) / (plt.3.349.cv + plt.35.399.cv) / (plt.4.449.cv + plot_spacer()))

dev.off()
```

# Rolling window 

Make a rolling window function

```{r}
rollingwindow_many_mcr <- function(df_wide, plots, width) {
  df_wide %>% 
    filter(plot == plots[1]) %>% 
    select(-dataset, -site, -habitat, -plot) %>% 
    rename(Year = year) -> df_wide_2

  # initialize the dataframe
  # width is the rolling window width
  megadf <- rollapply(data = df_wide_2, 
                      width = width, 
                      by = 1, FUN = partitionR_window, 
                      by.column = FALSE, align = "left") %>% 
    as.data.frame() %>% 
    mutate(across(-warnings, as.numeric)) %>% 
    mutate(Community = plots[1])
  
  
  # iterate over each site
   for(i in 2:length(plots)) {
     # filter whole dataset
     df_wide %>% 
        filter(plot == plots[i]) %>% 
        select(-dataset, -site, -habitat, -plot) %>% 
        rename(Year = year) -> df_wide_3
        
        # apply rolling window    
         tmp <- rollapply(data = df_wide_3, 
                            width = width, 
                            by = 1, FUN = partitionR_window, 
                            by.column = FALSE, align = "left") %>% 
              as.data.frame() %>% 
              mutate(across(-warnings, as.numeric)) %>% 
              mutate(Community = plots[i])
         megadf <- rbind(megadf, tmp)
   }
  
  # add metadata
  megadf %>% 
    as.data.frame() %>% 
    rowwise() %>% 
    mutate(Site = paste0("LTER_", str_split(Community, "_")[[1]][2])) %>% 
    mutate(Habitat = str_split(Community, "_")[[1]][3])
}
    
```

And a plotting function

```{r}
plot_rollingwindow_mcr <- function(df_rolling) {
  # df_rolling is the output from the rollingwindow_many_mcr function
  df_rolling %>% 
    select(start_year, Community, CVe, CVtilde, CVa, CVc) %>% 
    pivot_longer(cols = c(CVe, CVtilde, CVa, CVc), names_to = "CV_type", values_to = "CV") %>% 
    ggplot(aes(x = start_year, y = CV)) +
    geom_line(aes(x = start_year, y = CV, group = CV_type, color = CV_type)) +
    ylab("CV") +
    xlab("First year of window") +
    scale_colour_viridis_d(name = "CV", labels = c("CVa" = expression("CV"[a]), 
                                                   "CVc" = expression("CV"[c]), 
                                                   "CVe" = expression("CV"[e]), 
                                                   "CVtilde" = expression(tilde("CV")))) +
      facet_wrap(.~Community) 
}

```


## 5-year window

Make one for a 5 year window

```{r}
mcr_rolling_wind_5 <- rollingwindow_many_mcr(df_wide = mcr_wide, plots = unique(mcr_wide$plot), width = 5)

plot_rollingwindow_mcr(mcr_rolling_wind_5) +
  plot_annotation(
    title = "5-year window",
    theme = theme(
      plot.title = element_text(face = "bold", vjust = 1.5),
    )
  ) -> plt.5yr
```

## 10-year window

```{r}
mcr_rolling_wind_10 <- rollingwindow_many_mcr(df_wide = mcr_wide, plots = unique(mcr_wide$plot), width = 10)

plot_rollingwindow_mcr(mcr_rolling_wind_10) +
  plot_annotation(
    title = "10-year window",
    theme = theme(
      plot.title = element_text(face = "bold", vjust = 1.5),
    )
  ) -> plt.10yr
```

## Print PDFs

```{r}
pdf(here("figures", "mcr_fish_moving_windows.pdf"), height = 14, width = 16)

print(plt.5yr)
print(plt.10yr)

dev.off()
```


## Zhao partition

```{r}
# do for LTER 1 forereef as an example
part_zhao_back1 <- zhao_decomp_w(subset_mcr_group(df_long = mcr_fish, 
                                                  meta_df = mcr_meta, 
                                                  filter_column = "plot", 
                                                  condition = "lter_1_forereef"))
```

# Plot mechanisms

```{r}
part_fore1 %>% 
  select(start_year, Delta, Psi, omega) %>% 
  pivot_longer(cols = c(Delta, Psi, omega), names_to = "Mechanism", values_to = "Value") %>% 
  ggplot(aes(x = start_year, y = Value)) +
  geom_line(aes(x = start_year, y = Value, group = Mechanism, color = Mechanism)) +
  ylab("Mechanism") +
  xlab("First year of window") 
```



Recall:
- CVa = CVcom with asynchrony only
- CVe = CV of an average species
- CVtilde = expected CVcom under assumption of perfect synchrony but realized dominance structure
- CVc is the temporal CV

## Look at all of the power law relationships for any window size

```{r}
plot_TPL(backreef_1, window_size = 15, ny = 1, form = "vari")
```






